Sample size

### 2021-04-16 scripts/r/sample-size/sample-size.Rmd
:building_construction: - test simulations

if (file.exists(sample_file)) {
  sample_sims <- readRDS(sample_file)
} else {
  sample_sims <- tibble(
    n_teams = n_ts_qs$n_teams,
    quants = n_ts_qs$quantiles,
    sd_team = map2(
      n_teams, quants,
      ~run_simulations(.x, .y)
    )
  )

  saveRDS(sample_sims, sample_file)
}
```

```{r plot, eval=FALSE, include=FALSE}
sample_sims <- sample_sims %>%
  mutate(
    cri = map(sd_team, function(.x) .x$random$team[4] - .x$random$team[3]) %>% unlist()
  )

>>>>

if (file.exists(sample_file)) {
  sample_sims <- readRDS(sample_file)
} else {
  # sample_sims <- tibble(
  #   n_teams = n_ts_qs$n_teams,
  #   quants = n_ts_qs$quantiles,
  #   sd_team = map2(
  #     n_teams, quants,
  #     ~run_simulations(.x, .y)
  #   )
  # )
  # 
  # saveRDS(sample_sims, sample_file)
  print("why?")
}
```

```{r plot}
sample_sims <- sample_sims %>%
  mutate(
    cri = map(sd_team, function(.x) .x$random$team[4] - .x$random$team[3]) %>% unlist()
  )
